---
title: "clean-evolution-of-self--control-data"
author: "Charmi"
date: "11/1/2017"
output: github_document
params:
  csv_dir: ../data/csv
  clean_dir: ../data/cleaned
---

```{r hh-setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(readr)
```

## Purpose

This file imports the data from 

MacLeana, Evan L., et al (2014). The evolution of self-control. PNAS, 111(20), E2140-E2148. Retrieved from <http://dx.doi.org/10.1073/pnas.1323533111>

and tidies it up, creating a single data file with brain region as a variable.

The data have already been gathered and saved as separate CSVs by different sheets we made in excel in `r params$csv_dir`.

## Import CSVs and create merged data file

Here are the steps we want to do for all of the evolution-of-self-control-specific files:

1. Import the CSV from `../data/csv/<brain-area>.csv`
2. Delete the second row since it contains comments we do not need.
3. Rename the variables to be shorter and more transparent
4. Add a variable called `Brain_area` equal to `<brain-area>`.
5. Clean data fields with +/- char

```{r define-text-file-cleaning-functions}
# Use sed to drop " and ± characters from files
Drop_plus_minus <- function(fn) {
  new_fn <- paste0(fn, ".clean")
  sed_cmd <- paste0("sed \'NA' <", fn, " >", new_fn)
  system(sed_cmd)
}
```

```{r define-clean-dataframe-function}
# Import_clean_area_data <- function(fn) {
#   # Import and clean a file containing brain-area-specific data
#   # Returns a new data frame
#   df <- read.csv(file = fn, skip = 2)
#   df <- df[-1,] # Comments are now first row
#   names(df) <- c("Species", "Order", "Mass_g", "Mass_SD", 
#                  "N_neurons", "N_neurons_SD",
#                  "N_other", "N_other_SD",
#                  "Neurons_per_mg", "Neurons_per_mg_SD",
#                  "Other_per_mg", "Other_per_mg_SD",
#                  "Other_per_neuron", "Other_per_neuron_SD",
#                  "Source")
#   file_name <- strsplit(basename(fn), "\\.")[[1]][1]
#   df$Brain_area <- file_name
#   df
# }
```

If we map a file-specific function across a list of the files, we can merge the list into a single data frame using `Reduce()`.

```{r map-across-list-and-merge}
# Clean all csv's then drop whole_brain because it has different columns
# fl <- list.files(path = "../data/csv", pattern = "\\.csv$", full.names = TRUE)
# sapply(fl, Drop_plus_minus)
# 
# fl_clean <- list.files(path = "../data/csv", pattern = "\\.clean$", full.names = TRUE)
# fl_clean <- fl_clean[!(fl_clean %in% "../data/csv/whole_brain.csv.clean")]
# if (length(fl_clean)) {
#   df_list <- lapply(fl_clean, Import_clean_area_data)
#   df_merged <- Reduce(function(x,y) merge(x, y, all=TRUE), df_list)
# } else {
#   warning("File list empty.")
# }
```

Let's write this to a new, clean directory (`r params$clean_dir`)

```{r export-merged}
# write_csv(df_merged, path = "../data/cleaned/herculano-houtzel-all.csv")
```

## To-dos

- ~~This would be even cleaner if we dropped the "± " from the *_SD columns.~~ 2017-10-03
- Parameterize file names and paths.