---
title: "clean-evolution-of-self--control-data"
author: "Charmi & Rick"
date: "`r Sys.time()`"
output: github_document
params:
  csv_dir: ../data/csv
  clean_dir: ../data/cleaned
---

```{r hh-setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(readr)
library(dplyr)
library(magrittr)
library(tidyr)
library(forcats)
library(ggplot2)
```

## Purpose

This file imports the data from 

MacLean, Evan L., et al (2014). The evolution of self-control. PNAS, 111(20), E2140-E2148. Retrieved from <http://dx.doi.org/10.1073/pnas.1323533111> and <https://figshare.com/articles/MacLean_et_al_PNAS_2014_Self-Control_Data/5579335>

and tidies it up, creating a single data file.

The data have already been gathered and saved as separate CSVs by different sheets we made in excel in `r params$csv_dir`.

## Import CSVs and create merged data file

Here are the steps we want to do for tidying and combing two separate CSV files:

1. Import the CSV from `../data/csv/cog_task_avg_score.csv`
2. Include the cylinder task data and A.not.B.Task data in one column, and arrange by common name.
3. Clean out the '-' from subj_info file.
4. Import the CSV from `../data/csv/subj_info.csv`
5. Make a new column for task responses as 'Y' if '*' and 'N' if '-'.
6. Remove the old columns with '*' and '-' as input.
7. Merge cog_task_avg_score and subj_info together by Common.Name.


```{r cog_task_cleaning}
cog <- read_csv("../data/csv/cog_task_avg_score.csv")
cog<-cog %>%
       gather(Task, Score, Cylinder.Task: A.not.B.Task) %>% arrange(Common.Name)

#Cleaning out '-' from Score

cog$Score <- gsub('-',NA,cog$Score,fixed=TRUE)
cog$Score <- as.factor(cog$Score)

#Cleaning out '-' from Composite Score

cog$Composite.Score <- gsub('-',NA,cog$Composite.Score,fixed=TRUE)
cog$Composite.Score <- as.factor(cog$Composite.Score)
cog
```

```{r cleaning_subj_info}
sub_info <- read_csv("../data/csv/subj_info.csv")

names(sub_info)[1] <- "Common.Name"

A.not.B.Y <- sub_info$A.not.B == "*"
Cylinder.Y <- sub_info$Cylinder == "*"
sub_info$A.not.B.Y.N[A.not.B.Y] <- "Y"
sub_info$A.not.B.Y.N[!A.not.B.Y] <- "N"
sub_info$Cylinder.Y.N[Cylinder.Y] <- "Y"
sub_info$Cylinder.Y.N[!Cylinder.Y] <- "N"
sub_info <- sub_info %>% select(-A.not.B, -Cylinder)

sub_info
```

```{r merge_data}

merged <- left_join(cog, sub_info, by="Common.Name")
merged

```

```{r order_columns}

col_order <- c("Common.Name", "Latin.Name", "A.not.B.Y.N", "Cylinder.Y.N", "Task", "Score", "Composite.Score", "Sex", "Age", "Population", "Subject")
merged_new <- merged[,col_order]
merged_new

```

##Clean Cylinder and A-not-B CSV files

1. Import both the csv files
2. Change column names to make it shorter and more specific
3. Merge both data files to make one file altogether

```{r clean_task_files}

cyl_task <- read_csv("../data/csv/Cylinder.csv")
ab_task <- read_csv("../data/csv/A-not-B.csv")

colnames(cyl_task) <- c("Species", "Pop", "Sex", "Sub_no.", "Warmups", "Test_percent_correct", "first_corr", "second_corr")
colnames(ab_task) <- c("Species", "Pop", "Sex", "Sub_no.", "Trials", "Accuracy")
```

Now we will change the species names to make both dataframe equal

```{r change_Species_names}

cyl_task$Species <- sub("black lemur", "Black Lemur", cyl_task$Species)
ab_task$Species <- sub("Capuchin monkey", "Capuchin", ab_task$Species)
ab_task$Species <- sub("Fox Squirrel", "Fox squirrel", ab_task$Species)
cyl_task$Species <- sub("Golden Monkey", "Golden monkey", cyl_task$Species)
ab_task$Species <- sub("Mongolian Gerbil", "Mongolian gerbil", ab_task$Species)
cyl_task$Species <- sub("ruffed lemur", "Ruffed lemur", cyl_task$Species)
ab_task$Species <- sub("White Carnea Pigeon", "White Carneau Pigeon", ab_task$Species)
ab_task$Species <- sub("Canis latrans", "Coyote", ab_task$Species)
ab_task$Species <- sub("Elphas maximus", "Asian Elephant", ab_task$Species)

cyl_task <- cyl_task %>% arrange(Species, Sub_no.)
ab_task <- ab_task %>% arrange(Species, Sub_no.)

ab_task
cyl_task

```

Let's write this to a new, clean directory (`r params$clean_dir`)

```{r export-merged}
write_csv(merged_new, path = "../data/cleaned/cog_score_and_sub_info.csv")
```

##Update: Clean and merge the new dataset provided by Dr. Evan MacLean

```{r clean_indv}

indv_cyl <- read_csv("../data/csv/indiv_dat_cyl.csv")
indv_AB <- read_csv("../data/csv/indiv_dat_AB.csv")

indv_cyl$n_1st_correct <- (indv_cyl$`1st Half % Correct`/100*5)
indv_cyl$n_2nd_correct <- (indv_cyl$`2nd Half % Correct`/100*5)

indv_cyl$Age <- sub("M", "6", indv_cyl$Age)
indv_cyl$Age[381] <- sub("M", "11", indv_cyl$Age[381])
indv_cyl

<<<<<<< HEAD
indv_cyl <- gather(indv_cyl, key=Trial_type, value = N_trials, Warmups, `n_1st_correct`, `n_2nd_correct`)

=======
>>>>>>> b4453f8f21d9a4dddd4837c26de2be17fe0b5a5f
## Remove the redundant columns (1st Half, 2nd Half %, Test % correct)

indv_cyl$Species <- sub("black lemur", "Black Lemur", indv_cyl$Species)
indv_cyl$Species <- sub("Brown lemur", "Brown Lemur", indv_cyl$Species)
indv_cyl$Species <- sub("ruffed lemur", "Ruffed Lemur", indv_cyl$Species)
indv_AB$Species <- sub("Black lemur", "Black Lemur", indv_AB$Species)
indv_cyl$Sex <- sub("UNKOWN", "U", indv_cyl$Sex)
indv_cyl$Sex <- sub("Unkown", "U", indv_cyl$Sex)
indv_cyl$Sex <- sub("UNKNOWN", "U", indv_cyl$Sex)
indv_cyl$Sex <- sub("11", "M", indv_cyl$Sex)
indv_cyl$Sex <- sub("6", "M", indv_cyl$Sex)
indv_cyl

<<<<<<< HEAD
filter(indv_cyl, indv_cyl$Sex == "6" | indv_cyl$Sex == "11")
filter(indv_cyl, indv_cyl$Species == "White Carneau Pigeon")

unique(indv_cyl$Sex)
unique(indv_cyl$Age)

write_csv(indv_cyl, path = "../data/cleaned/cyl_indv.csv")
write_csv(indv_AB, path = "../data/cleaned/ab_indv.csv")



# write_csv(ab_task, path="../data/cleaned/ab_task.csv")
# write_csv(cyl_task, path="../data/cleaned/cyl_task.csv")
# 
# indv_cyl
```


=======
write_csv(indv_cyl, path = "../data/cleaned/cyl_indv.csv")
write_csv(indv_AB, path = "../data/cleaned/ab_indv.csv")

# write_csv(ab_task, path="../data/cleaned/ab_task.csv")
# write_csv(cyl_task, path="../data/cleaned/cyl_task.csv")
# 
# indv_cyl
```


>>>>>>> b4453f8f21d9a4dddd4837c26de2be17fe0b5a5f
```{r plot}

# p1 <- ggplot(data = indv_cyl) + aes(x = Trial_type, y = N_trials, color = Species, group_by(Species)) + geom_point() + geom_line()
# p1
<<<<<<< HEAD
x = 'M'
indv_cyl %>% filter(Species == 'Aye Aye', Sex == x) %>% ggplot() +
=======

indv_cyl %>% filter(Species == 'Aye Aye') %>% ggplot() +
>>>>>>> b4453f8f21d9a4dddd4837c26de2be17fe0b5a5f
  aes(x = Trial_type, y = N_trials, color = Name) +
  geom_point() +
  geom_line(aes(group = Name)) +
  # facet_grid(cols = vars(Sex)) +
  aes(x= fct_inorder(Trial_type))
```




