---
title: "clean-evolution-of-self--control-data"
author: "Charmi"
date: "11/1/2017"
output: github_document
params:
  csv_dir: ../data/csv
  clean_dir: ../data/cleaned
---

```{r hh-setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(readr)
library(dplyr)
library(magrittr)
library(tidyr)
```

## Purpose

This file imports the data from 

MacLeana, Evan L., et al (2014). The evolution of self-control. PNAS, 111(20), E2140-E2148. Retrieved from <http://dx.doi.org/10.1073/pnas.1323533111>

and tidies it up, creating a single data file with brain region as a variable.

The data have already been gathered and saved as separate CSVs by different sheets we made in excel in `r params$csv_dir`.

## Import CSVs and create merged data file

Here are the steps we want to do for tidying and combing two separate CSV files:

1. Import the CSV from `../data/csv/cog_task_avg_score.csv`
2. Include the cylinder task data and A.not.B.Task data in one column, and arrange by common name.
3. Clean out the '-' from subj_info file.

4. Import the CSV from `../data/csv/subj_info.csv`
5. Make a new column for task responses as 'Y' if '*' and 'N' if '-'.
6. Remove the old columns with '*' and '-' as input.
7. Merge cog_task_avg_score and subj_info together by Common.Name.


```{r cog_task_cleaning}
cog <- read_csv("../data/csv/cog_task_avg_score.csv")
cog<-cog %>%
       gather(Task, Score, Cylinder.Task: A.not.B.Task) %>% arrange(Common.Name)

#Cleaning out '-' from Score

cog$Score <- gsub('-',NA,cog$Score,fixed=TRUE)
cog$Score <- as.factor(cog$Score)

#Cleaning out '-' from Composite Score

cog$Composite.Score <- gsub('-',NA,cog$Composite.Score,fixed=TRUE)
cog$Composite.Score <- as.factor(cog$Composite.Score)
cog
```

```{r cleaning_subj_info}
sub_info <- read_csv("../data/csv/subj_info.csv")

names(sub_info)[1] <- "Common.Name"

A.not.B.Y <- sub_info$A.not.B == "*"
Cylinder.Y <- sub_info$Cylinder == "*"
sub_info$A.not.B.Y.N[A.not.B.Y] <- "Y"
sub_info$A.not.B.Y.N[!A.not.B.Y] <- "N"
sub_info$Cylinder.Y.N[Cylinder.Y] <- "Y"
sub_info$Cylinder.Y.N[!Cylinder.Y] <- "N"
sub_info <- sub_info %>% select(-A.not.B, -Cylinder)

sub_info
```

```{r merge_data}

merged <- left_join(cog, sub_info, by="Common.Name")
merged

```

```{r order_columns}

col_order <- c("Common.Name", "Latin.Name", "A.not.B.Y.N", "Cylinder.Y.N", "Task", "Score", "Composite.Score", "Sex", "Age", "Population", "Subject")
merged_new <- merged[,col_order]
merged_new

```


Let's write this to a new, clean directory (`r params$clean_dir`)

```{r export-merged}
write_csv(merged_new, path = "../data/cleaned/cog_score_and_sub_info.csv")
```



