---
title: "Herculano-Houtzel Data Dictionary"
output: github_document
---


```{r LoadFile, include=FALSE}

library("readr")

hh <- read.csv("../cleaned/herculano-houtzel-all.csv")
```

##Brain_areas

<b><i> Whole brain values provided in the data are a summation of data from cerebral cortex, cerebellum, and rest of the brain because olfactory bulb data was not always available.</b></i>

- Cerebral Cortex:
    - All structures lateral to the olfactory tract
    - Includes: Hippocampus and subcortical white matter

- Cerebellum:
    - Includes: Cerebellar cortex, subcortical white matter, and deep cerebellar nuclei
  
- Olfactory Bulb:
    - Not defined
    - Not available for all the species
    
- Rest of the Brain:
    - Brainstem, diencephelon, and striatum
    
----------------------------------------------------------------------

Most of the brain area measurements were performed from only one hemisphere. It was then multiplied by 2 to use as the final data.

----------------------------------------------------------------------

##Number of animals (Num_an) used for counting the neuronal numbers in each species


```{r ChangesInDataframe, echo=FALSE}


#Create a new column for number of animals used for each species
hh$Num_an <- NA

#Reorder the columns and remove all quantitative columns except SD ones
hh <- hh[c(1,2,16,17,15,4,6,8,10,12,14)]

```

```{r Change_Species_Name, echo=FALSE}

#Arrange animals alphabetically
hh <- hh[order(hh$Species),]

#Remove "n=" from the species' names
hh[48,1] = "Elephantulusmyurus"
hh[7,1] = "Antidorcasmarsupialis"
# hh[11,1] = "Aotustrivirgatus"
hh[15,1] = "Blarinabrevicauda"
hh[24,1] = "Caviaporcellus"
hh[31,1] = "Condyluracristata"
# hh[41,1] = "Dasyproctaprimnolopha"
hh[52,1] = "Giraffacamelopardalensis"
hh[57,1] = "Heterocephalusglaber"
hh[68,1] = "Loxodontaafricana"
# hh[75,1] = "Macacamulatta"
hh[82,1] = "Mesocricetusauratus"
# hh[86,1] = "Microcebusmurinus"
hh[90,1] = "Musmusculus"
hh[94,1] = "Oryctolaguscuniculus"
hh[98,1] = "Otolemurgarnetti"
hh[105,1] = "Parascalopsbreweri"
# hh[109,1] = "Petrodromustetradactylus"
# hh[114,1] = "Procaviacapensis"
# hh[118,1] = "Proechimyscayennensis"
hh[122,1] = "Rattusnorvegicus"
hh[129,1] = "Scalopusaquaticus"
hh[133,1] = "Sciuruscarolinensis"
hh[134,1] = "Sorexfumeus"
hh[138,1] = "Susscrofadomesticus"
hh[142,1] = "Tragelaphusstripceros"
# hh[146,1] = "Tupaiaglis"

write_csv(hh, path="hh-dict.csv")
hh <- read.csv("hh-dict.csv")
hh
```

```{r Add_num_of_animals, echo=FALSE}

hh[1,4] = 2
hh[2,4] = 2
hh[3,4] = 2
hh[42,4] = 1
hh[43,4] = 1
hh[44,4] = 1
hh[45,4] = 2
hh[46,4] = 2
hh[47,4] = 2
hh[48,4] = 2
hh[107,4] = 2
hh[108,4] = 2
hh[109,4] = 2
hh[110,4] = 2
hh[4,4] = 1
hh[5,4] = 1
hh[6,4] = 1
hh[7,4] = 1
hh[12,4] = 5
hh[13,4] = 5
hh[14,4] = 5
hh[15,4] = 5
hh[16,4] = 1
hh[17,4] = 1
hh[21,4] = 2
hh[22,4] = 2
hh[23,4] = 2
hh[24,4] = 2
hh[28,4] = 4
hh[29,4] = 4
hh[30,4] = 4
hh[31,4] = 4
hh[49,4] = 1
hh[50,4] = 1
hh[51,4] = 1
hh[52,4] = 1
hh[54,4] = 3
hh[55,4] = 3
hh[56,4] = 3
hh[57,4] = 3
hh[65,4] = 1
hh[66,4] = 1
hh[67,4] = 1
hh[68,4] = 1
hh[79,4] = 2
hh[80,4] = 2
hh[81,4] = 2
hh[82,4] = 2
hh[87,4] = 4
hh[88,4] = 4
hh[89,4] = 4
hh[90,4] = 4
hh[95,4] = 11
hh[96,4] = 11
hh[97,4] = 11
hh[98,4] = 11
hh[102,4] = 3
hh[103,4] = 3
hh[104,4] = 3
hh[105,4] = 3
hh[119,4] = 5
hh[120,4] = 5
hh[121,4] = 5
hh[122,4] = 5
hh[126,4] = 3
hh[127,4] = 3
hh[128,4] = 3
hh[129,4] = 3
hh[130,4] = 9
hh[131,4] = 9
hh[132,4] = 9
hh[133,4] = 9
hh[134,4] = 3
hh[135,4] = 1
hh[136,4] = 1
hh[137,4] = 1
hh[138,4] = 1
hh[139,4] = 1
hh[140,4] = 1
hh[141,4] = 1
hh[142,4] = 1


hh
write_csv(hh, path="hh-dict.csv")

```




| Species Name           | Order           | Number of animals | Brain Areas  |
|------------------------|-----------------|-------------------|-------------|
| Amblysomus hottentotus | Afrotheria      | 2                 | Neves et al |
| Dendrohyrax dorsalis   | Afrotheria      | 1                 | Neves et al |
| Elephantulus myurus    | Afrotheria      | 2                 | Neves et al |
| Petrodromus tetradactylus | Afrotheria   | 2                 | Neves et al |
| Procavia capensis      | Afrotheria      | 2                 | Neves et al |
| 6                      | Whole brain |