---
title: "Herculano-Houtzel Data Dictionary"
output: github_document
---


```{r LoadFile, include=FALSE}

library("readr")

hh <- read.csv("../cleaned/herculano-houtzel-all.csv")
```

##Brain_areas

<b><i> Whole brain values provided in the data are a summation of data from cerebral cortex, cerebellum, and rest of the brain because olfactory bulb data was not always available.</b></i>

- Cerebral Cortex:
    - All structures lateral to the olfactory tract
    - Includes: Hippocampus and subcortical white matter

- Cerebellum:
    - Includes: Cerebellar cortex, subcortical white matter, and deep cerebellar nuclei
  
- Olfactory Bulb:
    - Not defined
    - Not available for all the species
    
- Rest of the Brain:
    - Brainstem, diencephelon, and striatum
    


##Number of animals (Num_an) used for counting the neuronal numbers in each species


```{r ChangesInDataframe, echo=FALSE}


#Create a new column for number of animals used for each species
hh$Num_an <- NA

#Reorder the columns and remove all quantitative columns except SD ones
hh <- hh[c(1,2,16,17,15,4,6,8,10,12,14)]

```

```{r Change_Species_Name, echo=FALSE}

#Remove "n=" from the species' names

hh[125,1] = "Elephantulusmyurus"

#Arrange animals alphabetically
hh <- hh[order(hh$Species),]

hh
write_csv(hh, path="hh-dict.csv")
hh <- read.csv("hh-dict.csv")
```

```{r Add_num_of_animals, echo=FALSE}

hh[1,4] = 2
hh[2,4] = 2
hh[3,4] = 2
hh[34,4] = 1
hh[35,4] = 1
hh[36,4] = 1


hh

```




| Species Name           | Order           | Number of animals | Brain Areas  |
|------------------------|-----------------|-------------------|-------------|
| Amblysomus hottentotus | Afrotheria      | 2                 | Neves et al |
| Dendrohyrax dorsalis   | Afrotheria      | 1                 | Neves et al |
| Elephantulus myurus    | Afrotheria      | 2                 | Neves et al |
| Petrodromus tetradactylus | Afrotheria   | 2                 | Neves et al |
| Procavia capensis      | Afrotheria      | 2                 | Neves et al |
| 6                      | Whole brain |