---
title: "Herculano-Houtzel Data Dictionary"
output: github_document
---


```{r LoadFile, include=FALSE}

library("readr")

hh <- read.csv("../cleaned/herculano-houtzel-all.csv")
```

```{r}


#Create a new column for number of animals used for each species
hh$Num_an <- NA

#Reorder the columns and remove all quantitative columns except SD ones
hh <- hh[c(1,2,16,17,15,4,6,8,10,12,14)]

hh

```

##Number of animals used for counting the neuronal numbers in each species


| Species Name           | Order           | Number of animals | Brain Areas  |
|------------------------|-----------------|-------------------|-------------|
| Amblysomus hottentotus | Afrotheria      | 2                 | Neves et al |
| Dendrohyrax dorsalis   | Afrotheria      | 1                 | Neves et al |
| Elephantulus myurus    | Afrotheria      | 2                 | Neves et al |
| Petrodromus tetradactylus | Afrotheria   | 2                 | Neves et al |
| Procavia capensis      | Afrotheria      | 2                 | Neves et al |
| 6                      | Whole brain |