---
title: "Herculano-Houtzel Data Dictionary"
output: github_document
---


```{r LoadFile, include=FALSE}

library("readr")

hh <- read.csv("../cleaned/herculano-houtzel-all.csv")
```

##Brain_areas

<b><i> Whole brain values provided in the data are a summation of data from cerebral cortex, cerebellum, and rest of the brain because olfactory bulb data was not always available.</b></i>

- Cerebral Cortex:
    - All structures lateral to the olfactory tract
    - Includes: Hippocampus and subcortical white matter

- Cerebellum:
    - Includes: Cerebellar cortex, subcortical white matter, and deep cerebellar nuclei
  
- Olfactory Bulb:
    - Not defined
    - Not available for all the species
    
- Rest of the Brain:
    - Brainstem, diencephelon, and striatum
    


##Number of animals (Num_an) used for counting the neuronal numbers in each species


```{r ChangesInDataframe, echo=FALSE}


#Create a new column for number of animals used for each species
hh$Num_an <- NA

#Reorder the columns and remove all quantitative columns except SD ones
hh <- hh[c(1,2,16,17,15,4,6,8,10,12,14)]

```

```{r Change_Species_Name, echo=FALSE}

#Arrange animals alphabetically
hh <- hh[order(hh$Species),]

#Remove "n=" from the species' names
hh[48,1] = "Elephantulusmyurus"
hh[7,1] = "Antidorcasmarsupialis"
# hh[11,1] = "Aotustrivirgatus"
hh[15,1] = "Blarinabrevicauda"
hh[24,1] = "Caviaporcellus"
hh[31,1] = "Condyluracristata"
# hh[41,1] = "Dasyproctaprimnolopha"
# hh[15,1] = "Blarinabrevicauda"
# hh[15,1] = "Blarinabrevicauda"


write_csv(hh, path="hh-dict.csv")
hh <- read.csv("hh-dict.csv")
hh
```

```{r Add_num_of_animals, echo=FALSE}

hh[1,4] = 2
hh[2,4] = 2
hh[3,4] = 2
hh[42,4] = 1
hh[43,4] = 1
hh[44,4] = 1
hh[45,4] = 2
hh[46,4] = 2
hh[47,4] = 2
hh[48,4] = 2
hh[107,4] = 2
hh[108,4] = 2
hh[109,4] = 2
hh[110,4] = 2
hh[4,4] = 1
hh[5,4] = 1
hh[6,4] = 1
hh[7,4] = 1
hh[12,4] = 5
hh[13,4] = 5
hh[14,4] = 5
hh[15,4] = 5
hh[16,4] = 1
hh[17,4] = 1
hh[21,4] = 2
hh[22,4] = 2
hh[23,4] = 2
hh[24,4] = 2
hh[28,4] = 4
hh[29,4] = 4
hh[30,4] = 4
hh[31,4] = 4


hh
write_csv(hh, path="hh-dict.csv")

```




| Species Name           | Order           | Number of animals | Brain Areas  |
|------------------------|-----------------|-------------------|-------------|
| Amblysomus hottentotus | Afrotheria      | 2                 | Neves et al |
| Dendrohyrax dorsalis   | Afrotheria      | 1                 | Neves et al |
| Elephantulus myurus    | Afrotheria      | 2                 | Neves et al |
| Petrodromus tetradactylus | Afrotheria   | 2                 | Neves et al |
| Procavia capensis      | Afrotheria      | 2                 | Neves et al |
| 6                      | Whole brain |