---
title: "hh-paper-plots"
author: "Charmi Mehta"
date: "1/29/2018"
output:
  html_document:
    self_contained: FALSE

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(magrittr)
library(gdata)
library(ggrepel)
library(dplyr)
```

<center><h1> Goals </h1>
<br>
<i>Load data and separate into different brain areas</i> </center>

```{r}
#load data

hh <- read.csv("../data/cleaned/herculano-houtzel-all.csv")

#Separating different brain areas

cerebellum_dat <- hh[which(hh$Brain_area == 'cerebellum'),]
cerebral_ctx_dat <- hh[which(hh$Brain_area == 'cerebral_ctx'), ]
olf_bulb_dat <- hh[which(hh$Brain_area == 'olf_bulb'), ]
whole_brain_dat <- hh[which(hh$Brain_area == 'whole_brain'), ]
rest_of_brain_dat <- hh[which(hh$Brain_area == 'rest_of_brain'), ]

# cerebellum_dat
# cerebral_ctx_dat
# olf_bulb_dat
# whole_brain_dat
# rest_of_brain_dat

```

<center><h2> Plots </h2> </center>
<br>
<br>
<center> <i><h3> Plot without naked mole rat, but with house mouse</h3> </i>
<br>
*A better fit to the same data points is found when the mouse is included in the analysis (exponent, 1.699 ± 0.096, r2 = 0.975, p < 0.0001), and still excludes the naked mole-rat.*
</center>
<br>

```{r plot1, echo=FALSE, fig.align='center'}

glires_ctx <- cerebral_ctx_dat[which(cerebral_ctx_dat$Order == 'Glires'), ]
glires_ctx <- glires_ctx[glires_ctx$Species != "Heterocephalusglaber", ]

#define x and y axis variables

neur_glires_a <- log(glires_ctx$N_neurons)
wt_glires_a <- log(glires_ctx$Mass_g)

#Defining Q1, Q3, upperlimit, and lowerlimit of x-axis (Mass(g))

Quart_for_wt <- quantile(wt_glires_a)

Q3_for_wt <- Quart_for_wt[4]
Q1_for_wt <- Quart_for_wt[2]

upperlimit_for_wt <- Q3_for_wt + 1.5*IQR(wt_glires_a)
lowerlimit_for_wt <- Q1_for_wt - 1.5*IQR(wt_glires_a)

#Defining Q1, Q3, upperlimit, and lowerlimit of x-axis (Mass(g))

Quart_for_neur <- quantile(neur_glires_a)

Q3_for_neur <- Quart_for_neur[4]
Q1_for_neur <- Quart_for_neur[2]

upperlimit_for_neur <- Q3_for_neur + 1.5*IQR(neur_glires_a)
lowerlimit_for_neur <- Q1_for_neur - 1.5*IQR(neur_glires_a)

#Plot the data with outliers

glires_ctx %>%
    ggplot() +
    aes(x = neur_glires_a, y = wt_glires_a) +
    labs(x = "Log number of neurons", y = "Log structure mass (g)") +
    geom_point(col = ifelse((wt_glires_a > upperlimit_for_wt | 
                               neur_glires_a > upperlimit_for_neur | 
                               wt_glires_a < lowerlimit_for_wt | 
                               neur_glires_a < lowerlimit_for_neur), "red", "black")) +
    geom_smooth(method = "lm" ,color = "blue", size = 0.5) +
    geom_text_repel(aes(label = ifelse((wt_glires_a > upperlimit_for_wt | 
                                          neur_glires_a > upperlimit_for_neur | 
                                          wt_glires_a < lowerlimit_for_wt | 
                                          neur_glires_a < lowerlimit_for_neur), 
                                       paste0(Species), "")), col = "red")

```
<br>
<br>
<center> <i> <h3> Plot without naked mole rat and house mouse </h3></i>
<br>
*The power law that relates the mass of the cerebral cortex to its number of neurons calculated across glires species without the naked mole-rat and the mouse (exponent, 1.519 ± 0.112, r2 = 0.953, p < 0.0001) still includes the mouse (m) data point in its 95% confidence interval, but excludes the naked mole-rat.*
</center>
<br>

```{r plot2, echo=FALSE, fig.align='center'}

glires_ctx <- cerebral_ctx_dat[which(cerebral_ctx_dat$Order == 'Glires'), ]
glires_ctx <- glires_ctx[glires_ctx$Species != "Heterocephalusglaber", ]
glires_ctx <- glires_ctx[glires_ctx$Species != "Musmusculus", ]

#define x and y axis variables

neur_glires_a <- log(glires_ctx$N_neurons)
wt_glires_a <- log(glires_ctx$Mass_g)

#Defining Q1, Q3, upperlimit, and lowerlimit of x-axis (Mass(g))

Quart_for_wt <- quantile(wt_glires_a)

Q3_for_wt <- Quart_for_wt[4]
Q1_for_wt <- Quart_for_wt[2]

upperlimit_for_wt <- Q3_for_wt + 1.5*IQR(wt_glires_a)
lowerlimit_for_wt <- Q1_for_wt - 1.5*IQR(wt_glires_a)

#Defining Q1, Q3, upperlimit, and lowerlimit of x-axis (Mass(g))

Quart_for_neur <- quantile(neur_glires_a)

Q3_for_neur <- Quart_for_neur[4]
Q1_for_neur <- Quart_for_neur[2]

upperlimit_for_neur <- Q3_for_neur + 1.5*IQR(neur_glires_a)
lowerlimit_for_neur <- Q1_for_neur - 1.5*IQR(neur_glires_a)

#Plot the graph

glires_ctx %>%
    ggplot() +
    aes(x = glires_ctx$N_neurons, y = glires_ctx$Mass_g) +
    labs(x = "Log number of neurons", y = "Log structure mass (g)") + geom_point() +
    # geom_point(col = ifelse((wt_glires_a > upperlimit_for_wt | 
    #                            neur_glires_a > upperlimit_for_neur | 
    #                            wt_glires_a < lowerlimit_for_wt | 
    #                            neur_glires_a < lowerlimit_for_neur), "red", "black")) +
    geom_smooth(method = "lm" ,color = "green", size = 0.5) 
    # geom_text_repel(aes(label = ifelse((wt_glires_a > upperlimit_for_wt | 
    #                                       neur_glires_a > upperlimit_for_neur | 
    #                                       wt_glires_a < lowerlimit_for_wt | 
    #                                       neur_glires_a < lowerlimit_for_neur), 
    #                                    paste0(Species), "")), col = "red")

```

<br>
<br>
<center><i><h3> Number of Cerebellar Neurons Vs Number of Cerebral Cortex Neurons </h3></i>
<br>
*The elephant is a clear outlier to the relationship that describes the variation of the number of cerebellar neurons as a power law of the number of neurons in the cerebral cortex across all species, with exponent 1.007 ± 0.054 (r2 = 0.905, p < 0.0001), which is a linear relationship.*
</center>

```{r echo=FALSE, fig.align='center'}

#define a new dataset for this plot

cerebellum_dat <- cerebellum_dat[cerebellum_dat$Species != "Gorillagorilla", ]

cerebellum_neurons <- data.frame(cerebellum_dat$Species, cerebellum_dat$Order, cerebellum_dat$N_neurons)
cerebral_ctx_neurons <- data.frame(cerebral_ctx_dat$Species, cerebral_ctx_dat$Order, cerebral_ctx_dat$N_neurons)


N_Neurons_of_two <- data.frame(cerebral_ctx_neurons, cerebellum_neurons$cerebellum_dat.N_neurons)
names(N_Neurons_of_two) <- c("Species", "Order", "cerebral_ctx1", "cerebellum1")
N_Neurons_of_two
#Define the upper and lower limit of outliers for x- and y-axes

cerb_neur <- log(N_Neurons_of_two$cerebellum1)
cerb_ctx_neur <- log(N_Neurons_of_two$cerebral_ctx1)

##Defining Q1, Q3, upperlimit, and lowerlimit of x-axis (cerebellum)

# Quart_for_cerebellum1 <- quantile(cerb_neur)
# 
# Q3_for_cerebellum1 <- Quart_for_cerebellum1[4]
# Q1_for_cerebellum1 <- Quart_for_cerebellum1[2]
# 
# upperlimit_for_cerebellum1 <- Q3_for_cerebellum1 + 1.5*IQR(cerb_neur)
# lowerlimit_for_cerebellum1 <- Q1_for_cerebellum1 - 1.5*IQR(cerb_neur)

##Defining Q1, Q3, upperlimit, and lowerlimit of x-axis (cerebral cortex)

# Quart_for_cerebral_ctx1 <- quantile(cerb_ctx_neur)
# 
# Q3_for_cerebral_ctx1 <- Quart_for_cerebral_ctx1[4]
# Q1_for_cerebral_ctx1 <- Quart_for_cerebral_ctx1[2]
# 
# upperlimit_for_cerebral_ctx1 <- Q3_for_cerebral_ctx1 + 1.5*IQR(cerb_ctx_neur)
# lowerlimit_for_cerebral_ctx1 <- Q1_for_cerebral_ctx1 - 1.5*IQR(cerb_ctx_neur)

order <- N_Neurons_of_two$Order

#Plot the data with outliers

N_Neurons_of_two %>%
    ggplot() +
    aes(x = cerb_ctx_neur, y = cerb_neur, color = order) +
    labs(x = "Cerebral Cortex (log of # of Neurons)", y = "Cerebellum (log of # of Neurons)") +
    geom_point() +
    geom_smooth(method = "lm", color = "blue", size = 0.5) +
    geom_text_repel(aes(label = ifelse(N_Neurons_of_two$Species == "Loxodontaafricana", paste0("Elephant"), "")))+
    geom_text_repel(aes(label = ifelse(N_Neurons_of_two$Species == "Giraffacamelopardalensis", paste0("Giraffe"), "")))
    # geom_text_repel(aes(label = ifelse((cerb_neur > upperlimit_for_cerebellum1 |
    #                                     cerb_ctx_neur > upperlimit_for_cerebral_ctx1 |
    #                                     cerb_neur < lowerlimit_for_cerebellum1 |
    #                                     cerb_ctx_neur < lowerlimit_for_cerebral_ctx1),
    #                                     paste0(Species), "")), col = "red") +
    # geom_point(col = ifelse((cerb_neur > upperlimit_for_cerebellum1 |
    #                         cerb_ctx_neur> upperlimit_for_cerebral_ctx1),
    #                         "red", "black")) +
```













