---
title: "hh-paper-plots"
author: "Charmi Mehta"
date: "1/29/2018"
output:
  html_document:
    self_contained: FALSE

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(magrittr)
library(gdata)
library(ggrepel)
library(dplyr)
library(LearnBayes)
library(cowplot)
library(gridExtra)
library(grid)
library(lattice)
library(gtable)
```

<center><h1> Goals </h1>
<br>
<i>Load data and separate into different brain areas</i> </center>

```{r}
#load data

hh <- read.csv("../data/cleaned/herculano-houtzel-all.csv")

#Separating different brain areas

cerebellum_dat <- hh[which(hh$Brain_area == 'cerebellum'),]
cerebral_ctx_dat <- hh[which(hh$Brain_area == 'cerebral_ctx'), ]
olf_bulb_dat <- hh[which(hh$Brain_area == 'olf_bulb'), ]
whole_brain_dat <- hh[which(hh$Brain_area == 'whole_brain'), ]
rest_of_brain_dat <- hh[which(hh$Brain_area == 'rest_of_brain'), ]

# cerebellum_dat
# cerebral_ctx_dat
# olf_bulb_dat
# whole_brain_dat
# rest_of_brain_dat

```

<center><h2> Plots </h2> </center>
<br>
<br>
<center> <i><h3> Plot without naked mole rat, but with house mouse</h3> </i>
<br>
*A better fit to the same data points is found when the mouse is included in the analysis (exponent, 1.699 ± 0.096, r2 = 0.975, p < 0.0001), and still excludes the naked mole-rat.*
</center>
<br>

```{r plot1, echo=FALSE, fig.align='center'}

glires_ctx <- cerebral_ctx_dat[which(cerebral_ctx_dat$Order == 'Glires'), ]
glires_ctx_het <- subset(glires_ctx, Species == "Heterocephalusglaber")
glires_ctx <- glires_ctx[glires_ctx$Species != "Heterocephalusglaber", ]

Com_Nam <- c("Naked Mole Rat")
glires_ctx_het[c("Common_Name")] <- Com_Nam
glires_ctx_het

#define x and y axis variables

neur_glires_a <- log(glires_ctx$N_neurons)
wt_glires_a <- log(glires_ctx$Mass_g)

#Plot the data with outliers

# glires_ctx %>%
#     ggplot() +
#     aes(x = neur_glires_a, y = wt_glires_a) +
#     labs(x = "Log number of neurons", y = "Log structure mass (g)") +
#     geom_point() +
#     geom_smooth(method = "lm" ,color = "blue", size = 0.5) +
#     geom_point(data = glires_ctx_het, col='red') +
#     geom_text_repel(data = glires_ctx_het, aes(label = glires_ctx_het$Common_Name), col='red')


nmr_no <- ggplot(glires_ctx, aes(N_neurons, Mass_g)) +
  geom_point(data = glires_ctx, col = ifelse(glires_ctx$Species == "Musmusculus", 'blue', 'black')) +
  geom_smooth(method = "lm" ,color = "green", size = 0.5) +
  labs(x = "Number of neurons", y = "Structure Mass (g)") +
  geom_text_repel(data = glires_ctx, aes(label = ifelse(glires_ctx$Species == "Musmusculus", paste0("Mouse"), "")), col='blue', box.padding = unit(1, "lines")) +
  geom_point(data = glires_ctx_het, col='red') +
  geom_text_repel(data = glires_ctx_het, aes(label = glires_ctx_het$Common_Name), col='red', box.padding = unit(4, "lines"))

```
<br>
<br>
<center> <i> <h3> Plot without naked mole rat and house mouse </h3></i>
<br>
*The power law that relates the mass of the cerebral cortex to its number of neurons calculated across glires species without the naked mole-rat and the mouse (exponent, 1.519 ± 0.112, r2 = 0.953, p < 0.0001) still includes the mouse (m) data point in its 95% confidence interval, but excludes the naked mole-rat.*
</center>
<br>

```{r plot2, echo=FALSE, fig.align='center'}

glires_ctx <- cerebral_ctx_dat[which(cerebral_ctx_dat$Order == 'Glires'), ]
glires_ctx1 <- subset(glires_ctx, Species == "Heterocephalusglaber" | Species == "Musmusculus")
glires_ctx <- glires_ctx[glires_ctx$Species != "Heterocephalusglaber", ]
glires_ctx <- glires_ctx[glires_ctx$Species != "Musmusculus", ]

#Add a common name column
Com_Nam <- c("Naked Mole Rat", "Mouse")
glires_ctx1[c("Common_Name")] <- Com_Nam

glires_ctx1

#define x and y axis variables

neur_glires_a <- log(glires_ctx$N_neurons)
wt_glires_a <- log(glires_ctx$Mass_g)

#Plot the graph

no_nmr_no_mouse <- ggplot(glires_ctx, aes(N_neurons, Mass_g)) + 
    geom_point() +
    geom_smooth(method = "lm" ,color = "green", size = 0.5) +
    labs(x = "Number of neurons", y = "Structure Mass (g)") +
    geom_point(data = glires_ctx1, col=ifelse(glires_ctx1$Species == "Heterocephalusglaber", 'red', ifelse(glires_ctx1$Species == "Musmusculus", 'blue', 'black'))) +
    geom_text_repel(data = glires_ctx1, aes(label = glires_ctx1$Common_Name), col=ifelse(glires_ctx1$Species == "Heterocephalusglaber", 'red', ifelse(glires_ctx1$Species == "Musmusculus", 'blue', 'black')))
```

<br>
<br>
<center><i><h3> Number of Cerebellar Neurons Vs Number of Cerebral Cortex Neurons </h3></i>
<br>
*The elephant is a clear outlier to the relationship that describes the variation of the number of cerebellar neurons as a power law of the number of neurons in the cerebral cortex across all species, with exponent 1.007 ± 0.054 (r2 = 0.905, p < 0.0001), which is a linear relationship.*
</center>

```{r echo=FALSE, fig.align='center'}

#define a new dataset for this plot

cerebellum_dat <- cerebellum_dat[cerebellum_dat$Species != "Gorillagorilla", ]

cerebellum_neurons <- data.frame(cerebellum_dat$Species, cerebellum_dat$Order, cerebellum_dat$N_neurons)
cerebral_ctx_neurons <- data.frame(cerebral_ctx_dat$Species, cerebral_ctx_dat$Order, cerebral_ctx_dat$N_neurons)


N_Neurons_of_two <- data.frame(cerebral_ctx_neurons, cerebellum_neurons$cerebellum_dat.N_neurons)
names(N_Neurons_of_two) <- c("Species", "Order", "cerebral_ctx1", "cerebellum1")
N_Neurons_of_two

cerb_neur <- log(N_Neurons_of_two$cerebellum1)
cerb_ctx_neur <- log(N_Neurons_of_two$cerebral_ctx1)

order <- N_Neurons_of_two$Order

#Plot the data with outliers

cerebellum_vs_ctx <- N_Neurons_of_two %>%
    ggplot() +
    aes(x = cerb_ctx_neur, y = cerb_neur, color = order) +
    labs(x = "Cerebral Cortex (log of # of Neurons)", y = "Cerebellum (log of # of Neurons)") +
    geom_point() +
    geom_smooth(method = "lm", color = "blue", size = 0.5) +
    geom_text_repel(aes(label = ifelse(N_Neurons_of_two$Species == "Loxodontaafricana", paste0("Elephant"), "")))+
    geom_text_repel(aes(label = ifelse(N_Neurons_of_two$Species == "Giraffacamelopardalensis", paste0("Giraffe"), "")))
```
<br>
<br>

<center><i><h3>Number of neurons versus structure mass for each brain area </i></h3>
<br>
*New plot created by Dr. Gilmore and Charmi*</center>

```{r Brain_area_NeuronsVsMass, echo = FALSE, fig.align='center'}
# Plot with diff shape, color for brain areas
# Worked on in lab meeting 2017-10-19
final <- hh %>%
  select(Species, Mass_g, N_neurons, Brain_area) %>%
  group_by(Species) %>% 
  # mutate(Whole_brain_g = sum(Mass_g), Whole_brain_n = sum(N_neurons)) %>%
  ggplot() +
  aes(x=log(Mass_g), y=log(N_neurons), shape=Brain_area, color=Brain_area) +
  labs(x = "Log of structure mass (g)", y = "Log of number of neurons") +
  geom_smooth(method = "lm") +
  geom_point()
```

<center> Combining 3 plots </center>

```{r 3plots, echo=FALSE}

p1 <- ggplotGrob(cerebellum_vs_ctx)
p2 <- ggplotGrob(nmr_no)
p3 <- ggplotGrob(no_nmr_no_mouse)
# g <- rbind(g2, g3, size = "first")
# g$widths <- unit.pmax(g2$widths, g3$widths)
# grid.draw(rbind(g2, g3))

g <- grid.arrange(p1,p2,p3, layout_matrix = rbind(c(2,3),c(1,1)))
ggsave("3plots.png", plot = g)

# grid.arrange(
#   grobs = gl,
#   widths = c(1),
#   layout_matrix = rbind(c(cerebellum_vs_ctx), c(no_nmr_no_mouse),
#                         c(nmr_no))
# )

# par(mfrow = c(3, 1))  # 3 rows and 1 column
# no_nmr_no_mouse
# nmr_no
# cerebellum_vs_ctx
# par(mfrow=c(3,1))
# no_nmr_no_mouse
# no_nmr1
# cerebellum_vs_ctx
# p1 <- plot_grid(no_nmr_no_mouse, no_nmr1, cerebellum_vs_ctx, labels = "AUTO")
# save_plot("paper_plot1.png", p1, nrow = 3, ncol=2)
# p1

```
















```














