---
title: "gather-the-evolution-of-self--control-data"
author: "Charmi Mehta & Rick Gilmore"
date: "`Sys.time()`"
output: github_document
params:
  csv_dir: ../data/csv
  xlsx_dir: ../data/xlsx
  xlsx_fn: evolution-of-self--control.xlsx
---

```{r, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# if(!("install.load" %in% installed.packages()[,1])) {
#   install.packages("install.load")
# }
# library(install.load)
library("openxlsx")
library("readr")
```

## Aims

Download data from 

MacLeana, Evan L., et al (2014). The evolution of self-control. PNAS, 111(20), E2140-E2148. Retrieved from <http://dx.doi.org/10.1073/pnas.1323533111>

convert to excel sheets
and save as CSVs.

## Download

Data are at

<http://www.pnas.org/content/suppl/2014/04/17/1323533111.DCSupplemental>

```{r download-docx}
url1 <- "http://www.pnas.org/content/suppl/2014/04/17/1323533111.DCSupplemental/pnas.1323533111.st01.docx"
url2 <- "http://www.pnas.org/content/suppl/2014/04/17/1323533111.DCSupplemental/pnas.1323533111.st02.docx"
url3 <- "http://www.pnas.org/content/suppl/2014/04/17/1323533111.DCSupplemental/pnas.1323533111.st03.docx"
url4 <- "http://www.pnas.org/content/suppl/2014/04/17/1323533111.DCSupplemental/pnas.1323533111.st04.docx"
url5 <- "http://www.pnas.org/content/suppl/2014/04/17/1323533111.DCSupplemental/pnas.1323533111.st05.docx"
url6 <- "http://www.pnas.org/content/suppl/2014/04/17/1323533111.DCSupplemental/pnas.1323533111.st06.docx"
url7 <- "http://www.pnas.org/content/suppl/2014/04/17/1323533111.DCSupplemental/pnas.1323533111.st07.docx"
url8 <- "https://ndownloader.figshare.com/files/9700537"
url9 <- "https://ndownloader.figshare.com/files/9700540"

download.file(url1, destfile = "../data/docx/The-evolution-of-self--control1.docx")
download.file(url2, destfile = "../data/docx/The-evolution-of-self--control2.docx")
download.file(url3, destfile = "../data/docx/The-evolution-of-self--control3.docx")
download.file(url4, destfile = "../data/docx/The-evolution-of-self--control4.docx")
download.file(url5, destfile = "../data/docx/The-evolution-of-self--control5.docx")
download.file(url6, destfile = "../data/docx/The-evolution-of-self--control6.docx")
download.file(url7, destfile = "../data/docx/The-evolution-of-self--control7.docx")
download.file(url8, destfile = "../data/csv/A-not-B.csv")
download.file(url9, destfile = "../data/csv/Cylinder.csv")
```

## Open and make an excel file for the .docx data files

(Do not include the top comments on the .docx files, only copy and paste the tables)

**Name the excel file "The-evolution-of-self-control.xlsx" and upload it to** `r params$xlsx_dir`
   
There should be seven sheets:

| Sheet number |  Sheet name    |
|--------------|----------------|
| 1            | Anatomical Data|
| 2            | Primate Ecological Data|
| 3            | Test Locations         |
| 4            | Subject Information    |
| 5            | Average Score on Cognitive Task|
| 6            | Compare diff. pop. same species|
| 7            | Socioeco and performance|

```{r}
anatom_dat <- openxlsx::read.xlsx("../data/xlsx/The-evolution-of-self-control.xlsx", sheet=1)
primat_eco_dat <- openxlsx::read.xlsx("../data/xlsx/The-evolution-of-self-control.xlsx", sheet=2)
test_loc <- openxlsx::read.xlsx("../data/xlsx/The-evolution-of-self-control.xlsx", sheet=3)
subj_info <- openxlsx::read.xlsx("../data/xlsx/The-evolution-of-self-control.xlsx", sheet=4)
cog_task_avg_score <- openxlsx::read.xlsx("../data/xlsx/The-evolution-of-self-control.xlsx", sheet=5)
diff_pop_same_species <- openxlsx::read.xlsx("../data/xlsx/The-evolution-of-self-control.xlsx", sheet=6)
socioeco_and_perform <- openxlsx::read.xlsx("../data/xlsx/The-evolution-of-self-control.xlsx", sheet=7)
```

## Save the excel file as CSV

```{r save-csv}
write_csv(anatom_dat, path="../data/csv/anatom_dat.csv")
write_csv(primat_eco_dat, path="../data/csv/primat_eco_dat.csv")
write_csv(test_loc, path="../data/csv/test_loc.csv")
write_csv(subj_info, path="../data/csv/subj_info.csv")
write_csv(cog_task_avg_score, path="../data/csv/cog_task_avg_score.csv")
write_csv(diff_pop_same_species, path="../data/csv/diff_pop_same_species.csv")
write_csv(socioeco_and_perform, path="../data/csv/socioeco_and_perform.csv")
```

## To-dos

1. Check if data paths exist before reading and writing.
2. Check if packages installed, if not, install and load.
3. Parameterize file names.

