---
title: "gather-herculano-houzel-etal-2015"
author: "Rick Gilmore"
date: "`r Sys.time()`"
output: github_document
params:
  csv_dir: ../data/csv
  xlsx_dir: ../data/xlsx
  xlsx_fn: herculano-houzel-etal-2015.xlsx
---

```{r, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# if(!("install.load" %in% installed.packages()[,1])) {
#   install.packages("install.load")
# }
# library(install.load)
library("openxlsx")
library("readr")
```

## Aims

Download data from 

Herculano-Houzel, S., Catania, K., Manger, P. R., & Kaas, J. H. (2015). Mammalian Brains Are Made of These: A Dataset of the Numbers and Densities of Neuronal and Nonneuronal Cells in the Brain of Glires, Primates, Scandentia, Eulipotyphlans, Afrotherians and Artiodactyls, and Their Relationship with Body Mass. Brain, behavior and evolution, 86(3-4), 145–163. Retrieved from <http://dx.doi.org/10.1159/000437413>

and save as CSVs.

## Download

Data are at 

<http://www.suzanaherculanohouzel.com/storage/Dataset%20for%20website.xlsx>.

```{r download-xlsx}
url <- "http://www.suzanaherculanohouzel.com/storage/Dataset%20for%20website.xlsx"
download.file(url, destfile = "../data/xlsx/herculano-houzel-etal-2015.xlsx")
```

## Open and Examine

There are five sheets:

| Sheet number | Sheet name |
|--------------|------------|
| 1            | Info       |
| 2            | Cerebral cortex |
| 3            | Cerebellum      |
| 4            | Rest of brain   |
| 5            | Olfactory bulb  |
| 6            | Whole brain |

```{r}
cerebral_ctx <- openxlsx::read.xlsx("../data/xlsx/herculano-houzel-etal-2015.xlsx", sheet=2)
cerebellum <- openxlsx::read.xlsx("../data/xlsx/herculano-houzel-etal-2015.xlsx", sheet=3)
rest_of_brain <- openxlsx::read.xlsx("../data/xlsx/herculano-houzel-etal-2015.xlsx", sheet=4)
olf_bulb <- openxlsx::read.xlsx("../data/xlsx/herculano-houzel-etal-2015.xlsx", sheet=5)
whole_brain <- openxlsx::read.xlsx("../data/xlsx/herculano-houzel-etal-2015.xlsx", sheet=6)
```

## Save as CSV

```{r save-csv}
write_csv(cerebral_ctx, path="../data/csv/cerebral_ctx.csv")
write_csv(cerebellum, path="../data/csv/cerebellum.csv")
write_csv(rest_of_brain, path="../data/csv/rest_of_brain.csv")
write_csv(olf_bulb, path="../data/csv/olf_bulb.csv")
write_csv(whole_brain, path="../data/csv/whole_brain.csv")
```

## To-dos

1. Check if data paths exist before reading and writing.
2. Check if packages installed, if not, install and load.
3. Parameterize file names.
